Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2022-05-16 2022/eamt/eamt-latex/eamt22.tex

These situations have been amply documented from a theoretical perspective \ \cite{Mansour09multiple,Mansour09domainadaptation,Hoffman18algorithms}. A general recommendation in the DA setting is to adjust the sampling distribution used to optimize the system so as to compensate for the mismatch between $\mathcal{D}^s(x)$ and $\mathcal{D}^t(x)$. This can be approximated by reweighting instances, or more conveniently domains, which are selected during training with a probability $\lambda^{l}(d)$, with $\lambda^{l}(d) \neq \lambda^{s}(d)$.

@@

Multidomain NMT (MDMT) aims to develop systems that simultaneously bode well for several domains. Like for DA, techniques for supervised MDMT combine one or several ingredients: (a) the specialization of data representations \cite{Kobus17domaincontrol} or of sub-networks \cite{Pham19generic} to differentiate the processing of each domain; (b) the use of adversarial techniques to neutralize differences between domains \cite{Britz17mixing}; (c) the use of automatic domain identification \cite{Jiang19multidomain}. Unsupervised MDMT is studied in \newcite{Farajian17multidomain}, as an instance of unsupervised DA.

>>>>

These situations have been amply documented from a theoretical perspective \cite{Mansour09multiple,Mansour09domainadaptation,Hoffman18algorithms}. A general recommendation in the DA setting is to adjust the sampling distribution used to optimize the system so as to compensate for the mismatch between $\mathcal{D}^s(x)$ and $\mathcal{D}^t(x)$. This can be approximated by reweighting instances, or more conveniently domains, which are selected during training with a probability $\lambda^{l}(d)$, with $\lambda^{l}(d) \neq \lambda^{s}(d)$.

@@

Multidomain NMT (MDMT) aims to develop systems that simultaneously bode well for several domains. Like for DA, techniques for supervised MDMT combine one or several ingredients: (a) the specialization of data representations \cite{Kobus17domaincontrol} or of sub-networks \cite{Pham19generic} to differentiate the processing of each domain; (b) the use of adversarial techniques to neutralize differences between domains \cite{Britz17mixing,Zeng18multidomain}; (c) the use of automatic domain identification e.g.\ \cite{Jiang19multidomain}. Unsupervised MDMT is studied in \cite{Farajian17multidomain}, as an instance of unsupervised DA.
